Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-28 ms.tex
I added descriptions and plots for new times series on UT2016-06-14 and UT2016-07-14.

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotAug12}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
\end{centering}
\end{figure}

>>>>

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotJun12}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotJun12}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotJun14}
\end{centering}
\end{figure}

I experimented with a whole new set of reference stars (shown in Figure \ref{fig:newRefStars}) to see if they would work better for the time series on UT 2016-06-14.
I ended up with a very similar time series, as see in Figure \ref{fig:refCorrectedPhotJun14newStars}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/st_labels}
\caption{A new set of reference stars that matched the source better in terms of brightness.}\label{fig:newRefStars}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/refcor_01}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14, using a new set of reference stars shown in Figure \ref{fig:newRefStars}.}\label{fig:refCorrectedPhotJun14newStars}
\end{centering}
\end{figure}

The time series from UT2016-07-14 showed a sharp drop in flux for all stars as seen in Figure \ref{fig:ut2016-07-14clouds}.
Turns out is clouds, as visible in Figure \ref{fig:ut2016-07-14cloudImg}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/ut2016_07_14_tser_allstars.pdf}
\caption{All stars' photometry for \shStar\ on UT 2016-07-14.
There is a sharp drop in flux at 32.88 due to clouds}\label{fig:ut2016-07-14clouds}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_162.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_166.pdf}
\caption{Three example images during a cloud passage.}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}
